Type Error Telemetry at Scale: Pseudonymized and Stochiastic

### 2023-09-17 programming23/paper.tex
session size

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\stddev}[1]{[#1\textsc{k}]}
\newcommand{\gcell}[1]{\cellcolor{green!20}#1}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}
\newcommand{\gbox}[1]{\colorbox{green!20}{#1}}
\newcommand{\ybox}[1]{\colorbox{yellow!18}{#1\vphantom{Ap}}}
\newcommand{\obox}[1]{\colorbox{orange!29}{#1\vphantom{Ap}}}
\newcommand{\rbox}[1]{\colorbox{red!30}{#1\vphantom{Ap}}}

@@

  \begin{tabular}{l@{}r@{~}l@{}r@{~}l@{}r@{~}l}
                 & Files  &              &     Lines &             &    Edit Range & \\
    Mean [std]   & 11,911 & \stddev{12}  &     6,497 & \stddev{22} &         3,680 & \stddev{31} \\
    Median       &  7,678 &              &     3,115 &             &           926 & \\
    \pct{99}     & 51,761 &              &    50,547 &             &        34,725 & \\
    & \includegraphics[width=0.2\columnwidth]{img/files-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}

@@

\Cref{f:codebase-size} summarizes the size of projects in the dataset.
The top half of the figure reports the mean, standard deviation, median,
and {99}th percentile for the number of files, lines, and lines in edit range.
The bottom half shows zoomed-in distributions of the file, line, and edit range
numbers.
For example, the x-axis of the first plot ranges from 0 to 1,000 files and
the y-axis counts up to 1,000 telemetry records.

@@

@@

  \begin{subfigure}[t]{\columnwidth}
    %% NOTE max time = 1 million seconds = 15 days ...  +100 are over 2 days

    \begin{tabular}{l@{}r@{~}l@{}r@{~}l} \\
                   & Time Span (sec)  &       & Record Count  \\
      Mean [std]   &     3,184 & \stddev{16}  &     286 & [583] \\
      Median       &       845 &              &     138        \\
      \pct{99}     &    35,450 &              &   3,302        \\
      & \includegraphics[width=0.2\columnwidth]{img/timespan-distribution.pdf}
      & & \includegraphics[width=0.2\columnwidth]{img/event-count-distribution.pdf}

    \caption{Session length in seconds and in number of records}
    \label{f:sessions-size}
  \end{subfigure}

  \caption{Dataset overview}
  \label{f:dataset-overview}
\end{figure}

>>>>

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}
\newcommand{\percentile}[1]{{#1}th~percentile}
\newcommand{\modefont}[1]{\texttt{#1}}
\newcommand{\mnocheck}{\modefont{nocheck}}
\newcommand{\mnonstrict}{\modefont{nonstrict}}
\newcommand{\mstrict}{\modefont{strict}}
\newcommand{\zerowidth}[1]{\makebox[0pt][l]{#1}}
\newcommand{\stddev}[1]{[#1\textsc{k}]}
\newcommand{\gcell}[1]{\cellcolor{green!20}#1}
\newcommand{\ycell}[1]{\cellcolor{yellow!18}#1}
\newcommand{\ocell}[1]{\cellcolor{orange!29}#1}
\newcommand{\rcell}[1]{\cellcolor{red!30}$\!\!$#1$\!\!$}
\newcommand{\gbox}[1]{\colorbox{green!20}{#1}}
\newcommand{\ybox}[1]{\colorbox{yellow!18}{#1\vphantom{Ap}}}
\newcommand{\obox}[1]{\colorbox{orange!29}{#1\vphantom{Ap}}}
\newcommand{\rbox}[1]{\colorbox{red!30}{#1\vphantom{Ap}}}

@@

  \begin{tabular}{l@{}r@{~}l@{}r@{~}l@{}r@{~}l}
                 & Files  &              &     Lines &             &    Edit Range & \\
    Mean [std]   & 11,911 & \stddev{12}  &     6,497 & \stddev{22} &         3,680 & \stddev{31} \\
    Median       &  7,678 &              &     3,115 &             &           926 & \\
    \pct{99}     & 51,761 &              &    50,547 &             &        34,725 & \\
    %% TODO x-axis starts at 1, not zero ... there are no zeros right??!
    & \includegraphics[width=0.2\columnwidth]{img/files-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/lines-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/editrange-distribution.pdf}

@@

\Cref{f:codebase-size} summarizes the size of projects in the dataset.
The top half of the figure reports the mean, standard deviation, median,
and \percentile{99} for the number of files, lines, and lines in edit range.
The bottom half shows zoomed-in distributions of the file, line, and edit range
numbers.
For example, the x-axis of the first plot ranges from 0 to 1,000 files and
the y-axis counts up to 1,000 telemetry records.

@@

\subsection{Session Size}

\begin{figure}[t]
  %% NOTE max time = 1 million seconds = 15 days ...  +100 are over 2 days

  \begin{tabular}{l@{}r@{~}l@{}r@{~}l} \\
                 & Time Span (sec)  &       & Record Count  \\
    Mean [std]   &     3,184 & \stddev{16}  &     286 & [583] \\
    Median       &       845 &              &     138        \\
    \pct{99}     &    35,450 &              &   3,302        \\
    %% TODO x-axis starts at 1, not zero ... there are no zeros right??!
    & \includegraphics[width=0.2\columnwidth]{img/timespan-distribution.pdf}
    & & \includegraphics[width=0.2\columnwidth]{img/event-count-distribution.pdf}

  \caption{Session size in seconds and in number of records}
  \label{f:session-size}
\end{figure}

FILL say more about why this data is interesting. What's the significance?

\Cref{f:session-size} outlines the size of the Roblox Studio sessions in the
data.
There are two useful notions of size: real time in seconds (between the first
and last record) and the total number of records.
The top of~\cref{f:session-size} reports the mean, standard deviation,
median, and \percentile{99}; the bottom shows size distributions, zoomed in
to focus on at most 1,000 units (x-axis) and 1,000 sessions (y-axis).

Similar to the data on project size, there is huge variation in session
length.
The longest sessions last several days and/or contain thousands of records,
while the shortest last a few milliseconds or include just one record.
Likewise, both plots in the figure follow a power-law distribution
(especially for record count).
The median session time is approximately 14 minutes.
The median number of
records is 138.
These numbers are reasonable.

@@

  \caption{FILL Type analysis overview}
  \label{f:dataset-overview}
\end{figure}
